IJAR Bayesian Nonparametrics Special Issue Manuscript

### 2015-09-27 ijar-npb-ms.tex
nz and yz parametrization

The set of functioning probabilities $p^k_t$
corresponding to a choosen set of time points ($t \in \{t_1, \ldots, \tmax\}$)
defines a discrete failure time distribution for components of type $k$,
$R^k(t) = p^k_{t_j}$, $t \in [t_j, t_{j+1})$.

@@

in terms of $\nz$, $\yz$

***Illustration prior-data conflict with $\bebin$?

>>>>

The set of functioning probabilities $p^k_t$
corresponding to a choosen set of time points ($t \in {\cal T} = \{t_1, \ldots, \tmax\}$)
defines a discrete failure time distribution for components of type $k$,
$R^k(t) = p^k_{t_j}$, $t \in [t_j, t_{j+1})$.

@@

For each component type $k$, we have to choose $2 \times |{\cal T}|$
parameters to specify the prior distribution for the discrete survival function of $T^k_i$,
so in total $2 \times |{\cal T}| \times K$ parameters.

Let us drop the super- and subscript $k$ and $t$ for a while
to discuss the role and interpretation of the parameters $\alpha$ and $\beta$
for each $k$ and $t$.
The Beta distribution is usually parametrized in terms of $\alpha$ and $\beta$ as used above, 
but for our generalization to sets of priors,
we suggest to use a different parametrization in terms of $\nz$, $\yz$:
\begin{align*}
\nz &= \alpha + \beta &
\yz &= \frac{\alpha}{\alpha + \beta} \,,
\end{align*}
or vice versa, $\alpha = \nz\yz$ and $\beta = \nz(1-\yz)$.
From the properties of the Beta distribution,
we see that $\yz$ is the prior mean for the functioning probability $p$,
and the higher $\nz$, the more probability weight will be concentrated around that mean.
Furthermore, $\nz$ can be interpreted as a pseudocount or prior strength,
this will be illustrated through revisting the posterior
based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$:

$p \mid s$ is Beta distributed with the updated parameters
\begin{align*}
\nn &= \nz + n &
\yn &= \frac{\nz}{\nz + n} \cdot \yz + \frac{n}{\nz + n} \cdot \frac{s}{n}\,,
\end{align*}
so after seeing that $s$ out of $n$ components function (at time $t$),
the posterior mean $\yn$ for $p$ is a weighted average of
the prior mean $\yz$ and $s/n$ (the fraction of function components in the data),
with the weights $\nz$ and $n$, respectively.
We see that $\nz$ plays the same role for the prior mean $\yz$
as the sample size $n$ for the observed mean $s/n$,
thus the notion of pseudocount.
Also, the higher $\nz$, the higher the weight for $\yz$
in the weighted average calculation of $\yn$,
so $\nz$ gives the strength of the prior as compared to the sample size $n$.
%The parameters $\nz$ and $\yz$ have a more intuitive interprtation,

The Beta-binomial distribution in terms of the updated parameters $\nn$ and $\yn$
is therefore
\begin{align*}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn\yn, m_k - l_k + \nn(1-\yn))}
                                                    {B(\nn\yn, \nn(1-\yn))} \,.
\end{align*}

The reparametrization enables us to see that in the conjugate setting,
learning from data amounts to averaging between prior and data.
While this allows for the tractability of the model,
it also comes with a serious drawback:
When prior and data are

***Illustration prior-data conflict with $\bebin$
